---
title: "10.2 Clustering"
author: "Shaquiel Pashtunyar"
date: "2022-08-11"
output:
  word_document: default
  pdf_document: default
---

```{r DataFrames, include=FALSE}
#import data sets
setwd("C:/Users/spashtunyar/Documents/school/DSC0520/")
binary_df <- read.csv("data/binary-classifier-data.csv")

trinary_df <- read.csv("data/trinary-classifier-data.csv")

#scatterplots
library("ggplot2")
```

## Scatterplots of both data sets

```{r Data frames, echo=FALSE}
ggplot(binary_df, aes(x=x, y=y, color=label))+geom_point()+ggtitle("Binary Data")

ggplot(trinary_df, aes(x=x, y=y, color=label))+geom_point()+ggtitle("Trianry Data")
```

# Fit a k nearest neighbors’ model for each dataset for k=3, k=5, k=10, k=15, k=20, and k=25. Compute the accuracy of the resulting models for each value of k. 
# Plot the results in a graph where the x-axis is the different values of k and the y-axis is the accuracy of the model.

```{r DataFrames2, include=FALSE}
library(useful)

#drop label
binaryclustering <- binary_df[, which(names(binary_df) !="label")]
Trinaryclustering <- trinary_df[, which(names(binary_df) !="label")]
set.seed(1500)
#plotting binary 3,5,10,15,20,25
binaryK3 <- kmeans(x=binaryclustering,centers = 3)
binaryK5 <- kmeans(x=binaryclustering,centers = 5)
binaryK10 <- kmeans(x=binaryclustering,centers = 10)
binaryK15 <- kmeans(x=binaryclustering,centers = 15)
binaryK20 <- kmeans(x=binaryclustering,centers = 20)
binaryK25 <- kmeans(x=binaryclustering,centers = 25)
bestbinary <- FitKMeans(binaryclustering, max.clusters = 25, seed = 1500)

besttrinary <- FitKMeans(Trinaryclustering, max.clusters = 25, seed = 1500)

```

## Binary Plots

```{r Data frames3, echo=FALSE}


plot(binaryK3, data = binaryclustering, title = "Binary K3")
plot(binaryK5, data = binaryclustering, title = "Binary K5")
plot(binaryK10, data = binaryclustering, title = "Binary K10")
plot(binaryK15, data = binaryclustering, title = "Binary K15")
plot(binaryK20, data = binaryclustering, title = "Binary K20")
plot(binaryK25, data = binaryclustering, title = "Binary K25")

PlotHartigan(bestbinary, title = "Binary Hartigan")
```

The best number of clusters to use here is 12

## Trinary Hartigan
```{r Data frames4, echo=FALSE}
PlotHartigan(besttrinary)
```

20 is the best fit here


Q1 Just by lookinmg at the two scatterplots, we can see that the data doesn't really show a linear model, so a linear classifier would not be better
We can also see that each color clusters together in different regions

# Q4
```{r Data frames5, echo=FALSE}
clustering <- read.csv("data/clustering-data.csv")
K2 <- kmeans(x=clustering,centers = 2)
K3 <- kmeans(x=clustering,centers = 3)
K4 <- kmeans(x=clustering,centers = 4)
K5 <- kmeans(x=clustering,centers = 5)
K6 <- kmeans(x=clustering,centers = 6)
K7 <- kmeans(x=clustering,centers = 7)
K8 <- kmeans(x=clustering,centers = 8)
K9 <- kmeans(x=clustering,centers = 9)
K10 <- kmeans(x=clustering,centers = 10)
K11 <- kmeans(x=clustering,centers = 11)
K12 <- kmeans(x=clustering,centers = 12)
```

```{r Data frames6, echo=FALSE}
plot (K2, data = clustering)
plot (K3, data = clustering)
plot (K4, data = clustering)
plot (K5, data = clustering)
plot (K6, data = clustering)
plot (K7, data = clustering)
plot (K8, data = clustering)
plot (K9, data = clustering)
plot (K10, data = clustering)
plot (K11, data = clustering)
plot (K12, data = clustering)

euclidean<- function(a, b) sqrt(sum((a-b)^2))

euclidean(clustering$x, clustering$y)
```

At this point I do not know how to use the euclidean function exactly. I see it is telling me the distance of points, but how i get that number per cluster is unknown.

I am unsure how to proceed from here for questions 5 and 6. 
